---
title: "Chapter 04: Multiple Equation GMM"
author: "Lachlan Deer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chapter 01: Finite Sample Properties}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Application: Returns to Scale in Electricity Supply 

Load the `hayashir` package
```{r}
library(hayashir)
```

And other libraries we need for this chapter
```{r}
library(skimr) # summary stats
library(dplyr) # data manipulation
library(systemfit) # for fitting system of regressions
```

## The Data

Let's get a quick look at our data by looking at the first 10 rows:

```{r}
head(greene, 10)
```

## Table 4.3: Summary Statistics

```{r}
# assign the greene data to the object 'df'
df <- greene

df %>%
    mutate(output = output / 1e3) %>%
    select(output, labor_share, capital_share, fuel_share) %>%
    skim()
```

## Table 4.4: Regression parameters from 2 regression set up

Following the text, the two equations we want to estimate are:

First, specify the equations we want to estimate:

```{r}
eq1 <- labor_share ~ log(price_labor / price_fuel) + log(price_capital / price_fuel) + log(output) 
eq2 <- capital_share ~ log(price_labor / price_fuel) + log(price_capital / price_fuel) + log(output)
```

As Hayashi tells us, the unique symmetry restriction is then
```{r}
restrict <- c(
    "labor_log(price_capital/price_fuel) = capital_log(price_labor/price_fuel)"
)
```

We estimate with the `systemfit` function from the package with the same name:

```{r}
sur_results <- systemfit(list(labor = eq1, capital = eq2), 
                         method = "SUR", 
                         restrict.matrix = restrict,
                         data= df)
summary(sur_results)
```

Which yields approximately the same coefficients as in the text.

Then we can calculate estimates of the remaining coefficients using adding up restrictions, homogeneity and symmetry.
For example:
$$
\hat{\gamma}_{33} = \hat{\gamma}_{11} + 2 \hat{\gamma}_{12} + \hat{\gamma}_{22}
$$

So that
```{r}
gamma_11 <- sur_results$coefficients["labor_log(price_labor/price_fuel)"]
gamma_12 <- sur_results$coefficients["labor_log(price_capital/price_fuel)"]
gamma_22 <- sur_results$coefficients["capital_log(price_capital/price_fuel)"]

gamma_33 <- gamma_11 + 2 * gamma_12 + gamma_22

print(paste("gamma_33 is: ", round(gamma_33,3)))
```

### Getting the Covariance Matrix, $\Sigma$ py pooled OLS

Run the three regressions via pooled OLS.
The equations are:

```{r}
eq1a <- labor_share ~ log(price_labor) + log(price_capital) + log(price_fuel) + log(output) 
eq2a <- capital_share ~ log(price_labor) + log(price_capital) + log(price_fuel) + log(output)
eq3a <- fuel_share ~ log(price_labor) + log(price_capital) + log(price_fuel) + log(output)
```

Then estimate:
```{r}
pooled_ols <- systemfit(list(labor = eq1a, capital = eq2a, fuel = eq3a), 
                         method = "OLS", 
                         data= df)
summary(pooled_ols)
```

And extract the residual covariance matrix:

```{r}
pooled_ols$residCov
```

## Table 4.5: Substitution Elasticities

The cross elasticity (from eq 4.7.9) is:

$$
\eta_{jk} = \frac{\gamma_{jk} + s_j s_k}{s_j s_k}
$$

So we calculate these for each data point, and then find the mean in our data.
Let's do this for the labor-capital elasticity, $\eta_{12}$:

```{r}
# the coefficient we are after
gamma_12 <- sur_results$coefficients["labor_log(price_capital/price_fuel)"]

# the fitted values
fitted_vals <- fitted( sur_results)

elasticity <- fitted_vals %>%
    mutate(eta_12 = (gamma_12 + (labor * capital)) / (labor * capital) ) %>%
    summarise(eta_12 = mean(eta_12)) 

print(paste0("Capital-Labor elasticity is: ", round(elasticity$eta_12, 2)))
```
