---
title: "Chapter 01: Finite Sample Properties of OLS"
author: "Lachlan Deer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chapter 01: Finite Sample Properties}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Application: Returns to Scale in Electricity Supply 

Load the `hayashir` package
```{r}
library(hayashir)
```

## The Data

Let's get a quick look at our data by looking at the first 10 rows:

```{r}
head(nerlove, 10)
```

Some information about the variables in the data can be found in the documentation:

```{r}
?nerlove
```

And we can gain an understanding of the structure of our data by:

```{r}
str(nerlove)

```

And by using the `skim` command from the `skimr` package we can look at summary statistics:

```{r}
# install.packages("skimr")
library(skimr)

skim(nerlove)
```

## Testing Homogeneity of the cost function

### The Unrestricted Model
```{r}
unrestricted_ls <- log(total_cost) ~ log(output) + 
                    log(price_labor) + log(price_capital) + log(price_fuel)

model1 <- lm(unrestricted_ls, data = nerlove)
summary(model1)

```

Scale Coefficient:
```{r}
return_to_scale <- 1 / model1$coefficients[2]
print(return_to_scale)
```

t-stat:
The `car` package provides the `linearHypothesis` package which provides an easy way to test linear hypotheses:
```{r}
library(car)

linearHypothesis(model1, c("log(price_capital) = 0"))

# relationship between t and F = F = t^2
test_results <- linearHypothesis(model1, c("log(price_capital) = 0"))

# ie. same as above
t_stat <- sqrt(test_results$F)

```

### The Restricted Model

Following the book:
```{r}
restricted_ls <- log(total_cost/price_fuel) ~ log(output) +
                        log(price_labor/price_fuel) + log(price_capital / price_fuel) 

model2 <- lm(restricted_ls, data = nerlove)
summary(model2)
```

Next, Hayashi provides a routine to compute the F-stat to test the restriction.
First, we proceed as he instructs:

We can find SSR from the `anova function:`
```{r}
anova(model1)
```

We need to get SSR_u from model 1 and the denominator df.  The `anova()` function returns a `data.frame` from which we need to extract:
    
1. the SSR -  located in the last row of the `Sum_Sq` column
2. The degress of freedom - located in the last row of the `Df` column

To get them:
```{r}
anova_model1 <- anova(model1)
final_row_u <- nrow(nrow(anova_model1))

SSR_u <- anova_model1$`Sum Sq`[final_row_u]
df_resid_u <- anova_model1$Df[final_row_u]
```

and doing the same for the for the restricted model:
```{r}
anova_model2 <- anova(model2)
final_row_r <- nrow(nrow(anova_model2))

SSR_r <- anova_model2$`Sum Sq`[final_row_r]
df_resid_r <- anova_model2$Df[final_row_r]
```

Then our F-stat can be computed as:
```{r}
f_stat <- ( (SSR_r - SSR_u) / (df_resid_r - df_resid_u)) / (SSR_u / (df_resid_u))
print(paste("F stat is:", f_stat))
```

Which has a p-value of 
```{r}
pf(f_stat, df_resid_r - df_resid_u, df_resid_u, lower.tail = FALSE)
```


Alternatively, we can look at the F-stat versus a critical value.#
The critical value at 5% is
```{r}
qf(0.05, df_resid_r - df_resid_u, df_resid_u, lower.tail = FALSE)
```

## Testing Restrictions in an Easier way

Though instructive, that was kind of *complicated* ... 
a simpler version would be using the `linearHypothesis` function that we have already seen. 
We specifying the restriction we want to impose:

```{r}
linearHypothesis(model1, "log(price_labor) + log(price_capital) + log(price_fuel) = 1")
```

## Detour: a cautionary note on $R^2$

```{r}
scale_effect <- log(total_cost / output) ~ log(output ) + 
                    log(price_labor ) + log(price_capital ) + log(price_fuel)

model3 <- lm(scale_effect, data = nerlove)
summary(model3)
```

## Testing Constant Returns to Scale

```{r}
linearHypothesis(model2, "log(output) = 1")
```

Which again returns an F-stat. 
We can map that into a t-stat as follows:

```{r}
f_stat2 <- linearHypothesis(model2, "log(output) = 1")

t_stat2 <- sqrt(f_stat2$F[2])

print(paste("t stat is:", t_stat2))

```

## Importance of plotting residuals
The `car` package again helps us. 
`car` comes with a function `residualPlot` which will plot residuals 
    against fitted values (by default),
or against a specified variable, in our case `log(output)`
```{r, fig.height= 6, fig.width=6}
# residual plot comes from car package
residualPlot(model2, variable = "log(output)")
```
