---
title: "Chapter 02 - Large Sample Theory"
author: "Lachlan Deer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load Libraries
```{r}
library(hayashir)
library(ggplot2)
library(dplyr)
library(zoo)
```


## Inspecting the Data

```{r}
head(mishkin)
```


## Figure 2.3
First we construct a date variable and then calculate CPI inflation
The library `zoo` contains the function `as.yearmon()` 
    to construct dates containing only year and months.
```{r}

mishkin2 <- mishkin %>%
                mutate(time_period = as.yearmon(paste(year, month, sep = "-")),
                       cpi_inflation = (cpi/lag(cpi) - 1) * 100 * 12
                       )
                

```

Now we plot the data:

```{r, warning = FALSE, fig.height= 6, fig.width=6}
ggplot(mishkin2) +
    geom_line(aes(time_period, tbill_1, linetype = "tbill_1")) +
    geom_line(aes(time_period, cpi_inflation, linetype = "cpi_inflation")) +
    xlab("Date") +
    ylab("percent") +
    theme_bw() + 
    theme(legend.position="bottom") +
    scale_linetype_manual(name = element_blank(), 
                          values = c(tbill_1 = "solid", cpi_inflation = "dotted"),
                          labels = c("inflation rate", "1 month T-bill rate")
                          )
```

## Figure 2.4

Compute real interest rate:
```{r}
mishkin2 <- mishkin2 %>%
                mutate(real_rate = tbill_1 - cpi_inflation)

```

And now plot:
```{r, fig.height= 6, fig.width=6}
ggplot(mishkin2) +
    geom_line(aes(time_period, real_rate, linetype = "tbill_1")) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    xlab("Date") +
    ylab("percent") +
    theme_bw() + 
    theme(legend.position="none")
```

## Table 2.1
First we subset the data.
The relevant Date range is January 1953 to July 1971.

```{r}
fama <- mishkin2 %>%
            filter(between(as.yearmon(time_period), 
                           as.yearmon("Jan 1953"), 
                           as.yearmon("Jul 1971")
                           )
                   )

```

```{r}
library(skimr)
skim(fama$real_rate)
```
Then the ACF
```{r}
acf(fama$real_rate, lag.max = 12, plot = FALSE)
```

Then the Ljung Box Q tests (use the `portes` package for more flexibility)

```{r}
library(portes)
```

```{r}
LjungBox(fama$real_rate, lags = seq(1, 12))
```

## Is the Nominal Interest Rate the Optimal Predictor?

```{r}
model1 <- lm(cpi_inflation ~ tbill_1, data = fama)
summary(model1)
```

### How to get robust standard errors?

```{r}
library(sandwich)
library(lmtest)

coeftest(model1, vcov = vcovHC(model1, "HC0")) # white's
```


```{r}
library(car)

linearHypothesis(model1, "tbill_1 = 1", white.adjust = "hc0")
```
