---
title: "Chapter 06: Serial Correlation"
author: "Lachlan Deer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chapter 01: Finite Sample Properties}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Application: Forward Exchange Rates as Optimal Predictors 

Load the `hayashir` package
```{r}
library(hayashir)
```

And other libraries we need for this chapter
```{r}
library(dplyr) # data manipulation
library(ggplot2) # plotting
library(forecast) # time series plotting - Acf
library(sandwich) # HAC standard errors
library(lmtest)   
```

## The Data

Let's get a quick look at our data by looking at the first 10 rows:

```{r}
head(yen, 10)
```

## Figure 6.1: Forecast Error: Yen/Dollar

```{r}

ggplot(data = yen, aes(x = date, y = spot_30 - forward_30))+
    geom_line() +
    geom_hline(yintercept = 0, linetype="dashed", color = "red") +
    theme_bw()

```


## Figure 6.2: Correlogram of $s30 - f$, Yen/Dollar 

The `Acf` function from the `forecast` package will do what we need here:

```{r}
Acf(yen$spot_30 - yen$forward_30, lag.max = 40)
```


## Figure 6.3: Yen/Dollar Spot Rate, Jan 1975 - Dec 1989

```{r}
ggplot(data = yen, aes(x = date, y = spot_rate))+
    geom_line() +
    scale_x_date(date_breaks = "3 years", date_labels =  "%m/%y") +
    theme_bw()
```

## Figure 6.4: Plot of $s30$ against $f$, Yen/Dollar

```{r}
ggplot(data = yen, aes(x = log(forward_30), y = log(spot_30)))+
    geom_point() +
    theme_bw()
```

## Table 6.2: Regression Tests for Market Efficiency

For the Yen/Dollar:

```{r}
mkt_eff <- lm (I(spot_30 - spot_rate) ~ I(forward_30 - spot_rate), data = yen)

summary(mkt_eff)

```

These results give standard errors under the assumption of heteroskedasticity. 
To correct for heteroskedasticity and autocorrelation we want HAC standard errors from the `sandwich` package.
In particular standard errors with a maximum of 4 lags that are not pre-whitened.
To get a summary of the regression we use the `coeftest` function from the `lm` package

```{r}
coeftest(mkt_eff, vcov = vcovHAC(mkt_eff, lag = 4, prewhite = FALSE))
```

To test that $\beta_0 =0$ and $\beta_1 = 1$ we use the linearHypothesis function from `car`

```{r}
linearHypothesis(mkt_eff, c("(Intercept) = 0", "I(forward_30 - spot_rate) = 1"),
                 vcov = vcovHAC(mkt_eff, lag = 4, prewhite = FALSE))
```

## Figure 6.5: Plot of $s30-s$ against $f - s$, Yen/Dollar

```{r}
ggplot(data = yen, aes(x = forward_30 - spot_rate, y = spot_30 - spot_rate))+
    geom_point() +
    geom_smooth(method = "lm", se = FALSE, color = "red") +
    theme_bw()
```
