---
title: "Chapter 03: Single Equation GMM"
author: "Lachlan Deer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Loading Libraries

```{r, warning = FALSE}
library(hayashir)
library(dplyr)
library(stargazer)
library(AER)

```

## Inspecting the data

```{r}
str(griliches)

```

## Table 3.1

```{r, results = 'asis'}

to_summarize <- griliches %>%
                    select(age, education, log_wage, kww_score, iq_score, experience)

stargazer(as.data.frame(to_summarize), type = "html")

```
Notice that because we are using the Blackburn-Neumark data rather than copying the data from Griliches directly we get slightly different results.

## Table 3.2

First we estimate the three models.
We again expect slightly different results because (i) 
   we have different data than Griliches; and 
   (ii) the controls are slightly different - due to data availability.

```{r}
model1 <- lm(log_wage ~ education + 
                 experience + tenure +
                 southern_residence + lives_metro + 
                 age + I(age^2) + married, 
                 data = griliches)
model2 <- lm(log_wage ~ education + iq_score + 
                 experience + tenure +
                 southern_residence + lives_metro + 
                 age + I(age^2) + married, 
                 data = griliches)
model3 <- ivreg(log_wage ~ education + iq_score + 
                     experience + tenure +
                     southern_residence + lives_metro +  
                     age + I(age^2) + married | 
                     . -iq_score + kww_score + mothers_educ,
                    data = griliches)
```

Let's put them all into a table, we use Std Errors in parentheses,
    *not t-stats*:

```{r, results = 'asis'}

stargazer(model1, model2, model3, type = "html",
          keep = c("education", "iq_score", "experience",
                  "tenure")
          )

```
